---
title: "Assignment 2"
author: "NITHIN VARMA"
date: "10/6/2022"
output: html_document
---

```{r}
library(caret)
library(ISLR)
library(dplyr)
library(class)
```

```{r}
Universal <- read.csv("C:/Users/Kittu Varma/Downloads/UniversalBank.csv")
```


```{r}
#Performing a K-NN classification with all attributes except ID and ZIP code.
Universal$ID <- NULL
Universal$ZIP.Code <- NULL
summary(Universal)
Universal$Personal.Loan =  as.factor(Universal$Personal.Loan)
```

```{r}
#Dividing into training and validation
Model_norm <- preProcess(Universal[, -8],method = c("center", "scale"))
summary(Universal)
Universal_norm <- predict(Model_norm,Universal)
summary(Universal_norm)

Index_Train <- createDataPartition(Universal$Personal.Loan, p = 0.6, list = FALSE)
Train = Universal_norm[Index_Train,]
validation = Universal_norm[-Index_Train,]
```

```{r}
#Prediction of data
library(FNN)
to_Predict = data.frame(Age = 40, Experience = 10, Income = 84, Family = 2,
                     CCAvg = 2, Education = 1, Mortgage = 0, Securities.Account =
                       0, CD.Account = 0, Online = 1, CreditCard = 1)
print(to_Predict)
Predict_Norm <- predict(Model_norm,to_Predict)
Predictions <- knn(train= as.data.frame(Train[,1:7,9:12]),
                  test = as.data.frame(Predict_Norm[,1:7,9:12]),
                  cl= Train$Personal.Loan,
                  k=1)
```
```
#The customer is classified in classes "0","1"

```{r}
#QUESTION-2
set.seed(123)
Universal <- trainControl(method= "repeatedcv", number = 3, repeats = 2)
searchGrid = expand.grid(k=1:10)
knn.model = train(Personal.Loan~., data = Train, method = 'knn', tuneGrid = searchGrid,trControl = Universal)
knn.model
#The value of k is 3.This is the value that balances between overfitting and ignoring the predictor information
```

```{r}
#QUESTION-3
Universal_prediction <- predict(knn.model,validation)
confusionMatrix(Universal_prediction,validation$Personal.Loan)
#This matrix has a 94.5% accuracy.
#This the confusion matrix for the validation data that results from using the best k.
```


```{r}
#QUESTION-4
ForPredictNorm = data.frame(Age = 40, Experience = 10, Income = 84, Family = 2,
                              CCAvg = 2, Education = 1, Mortgage = 0,
                              Securities.Account =0, CD.Account = 0, Online = 1,
                              CreditCard = 1)
ForPredictNorm = predict(Model_norm, ForPredictNorm)
predict(knn.model, ForPredictNorm)
#It results in level 0,1
```

```{r}
#QUESTION-5
#Creating Training, Test, and validation sets from the data collection.
Train_size = 0.5 #training(50%)
Train_Index = createDataPartition(Universal_norm$Personal.Loan, p = 0.5, list = FALSE)
Train = Universal_norm[Train_Index,]

valid_size = 0.3 #validation(30%)
Validation_Index = createDataPartition(Universal_norm$Personal.Loan, p = 0.3, list = FALSE)
validation = Universal_norm[Validation_Index,]

Test_size = 0.2 #Test Data(20%)
Test_Index = createDataPartition(Universal_norm$Personal.Loan, p = 0.2, list = FALSE)
Test = Universal_norm[Test_Index,]


Trainingknn <- knn(train = Train[,-8], test = Train[,-8], cl = Train[,8], k =3)
Validknn <- knn(train = Train[,-8], test = validation[,-8], cl = Train[,8], k =3)
Testingknn <- knn(train = Train[,-8], test = Test[,-8], cl = Train[,8], k =3)

confusionMatrix(Trainingknn, Train[,8])
confusionMatrix(Validknn, validation[,8])
confusionMatrix(Testingknn, Test[,8])
```

#This is matrix and this is the whole assigment